Gompertzian growth as infinitely correlated non-local growth

### 2023-08-05 arxiv2/new_draft.tex
fix

In spite of the connection of the Gompertz model with higher order terms in a logistic model, it is still not clear whether the source of growth is external or internal. The right hand side ``resource'' term is not specific enough so as to specify the location of the source. However, one could argue that the since the Gompertz model has asymptoticaly infinite initial growth rate, the system could be seen as exposed to a ubiquitous signal that initiates the growth and subsequently decays exponentially just like a memoryless process. To further explore the source of growth we turn to the microscopic domain.

>>>>

In spite of the connection of the Gompertz model with higher order terms in a logistic model, it is still not clear whether the source of growth is external or internal. The right hand side ``resource'' term is not specific enough so as to specify the location of the source. However, one could argue that the since the Gompertz model has asymptotically infinite initial growth rate, the system could be seen as exposed to a ubiquitous signal that initiates the growth and subsequently decays exponentially just like a memoryless process. To further explore the source of growth we turn to the microscopic domain.
